Measuring the Influence of Twitter Bots during the 2018 US Midterm Election

### 2019-09-06 paper.tex
Removing the float package
Remove. Some more shit to do

\documentclass[letterpaper]{article}
\usepackage{aaai19}
\usepackage{times} 
\usepackage{helvet}
\usepackage{courier} 
\usepackage[hyphens]{url}
\usepackage{graphicx}
\urlstyle{rm}
\def\UrlFont{\rm}
\usepackage{graphicx}
\frenchspacing
\setlength{\pdfpagewidth}{8.5in}
\setlength{\pdfpageheight}{11in}

% custom packages%
\usepackage{amsmath}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{multirow}
\usepackage{subcaption}
\usepackage{float}

@@

\setcounter{secnumdepth}{0} %May be changed to 1 or 2 if section numbers are desired.

@@

\section{Methods}
\label{sec:method}
\subsection{Data Collection}
Twenty-nine manually identified keywords, names of 53 House candidates, and 27 Senate candidates were used to collect live data from Twitter. The manually defined keywords were:

\begin{itemize}
    \item 2018Midterms
    \item 2018MidtermElections
    \item Election2018
    \item ElectionDay
    \item MAGA2018
    \item MAGA
    \item Trump2020
    \item AmericaFirst
    \item TheResistance
    \item resist
    \item VoteThemOut
    \item 2018Senate
    \item VoteRed
    \item Voteblue
    \item WalkAwayFromDemocrats2018
    \item WalkAwayFromRepublicans2018
    \item VOTE
    \item GAEarlyVoting
    \item EarlyVoting
    \item plus1
    \item IVoted
    \item WinBlue
    \item WinRed
    \item BlueWave
    \item RedWave
    \item republican2018
    \item democrat2018
    \item Republican
    \item Democrat
\end{itemize}

House candidates were:

\begin{itemize}
    \item don young
    \item alyse s galvin
    \item katie hill
    \item steve knight
    \item katie porter
    \item mimi walters
    \item harley rouda
    \item dana rohrabacher
    \item michael waltz
    \item nancy soderberg
    \item mario diaz balart
    \item mary barzee flores
    \item karen c handel
    \item lucy mcbath
    \item cindy axne
    \item david young
    \item mike bost
    \item brendan kelly
    \item rodney davis
    \item betsy dirksen londrigan
    \item randy hultgren
    \item lauren underwood
    \item jared golden
    \item bruce poliquin
    \item william lacy clay jr
    \item greg gianforte
    \item kathleen williams
    \item george holding
    \item linda coleman
    \item ted budd
    \item kathy manning
    \item don bacon
    \item kara eastman
    \item tom malinowski
    \item leonard lance
    \item dina titus
    \item joyce bentley
    \item susie lee
    \item danny tarkanian
    \item pete king
    \item liuba grechen shirley
    \item chris collins
    \item nate mcmurray
    \item troy balderson
    \item danny o connor
    \item scott perry
    \item george scott
    \item pete sessions
    \item colin allred
    \item scott taylor
    \item elaine luria
    \item jaime herrera beutler
    \item carolyn long
\end{itemize}

Senate candidates were:

\begin{itemize}
    \item kyrsten sinema
    \item martha mcsally
    \item bill nelson
    \item rick scott
    \item joe donnelly
    \item mike braun
    \item tina smith
    \item karin housley
    \item claire mccaskill
    \item josh hawley
    \item cindy hyde smith
    \item mike espy
    \item chris mcdaniel
    \item jon tester
    \item matt rosendale
    \item kevin cramer
    \item heidi heitkamp
    \item robert menendez
    \item bob hugin
    \item dean heller
    \item jacky rosen
    \item marsha blackburn
    \item phil bredesen
    \item ted cruz
    \item beto o rourke
    \item joe manchin iii
    \item patrick morrisey
\end{itemize}

@@

\begin{table}[H]
    \centering
    \begin{tabular}{|l|l|}
    \hline
    \textbf{Word} & \textbf{Percentage Difference} \\ \hline
    voteredtosaveamerica & 169.715447 \\ \hline
    patriots & 161.121157 \\ \hline
    votered & 130.514988 \\ \hline
    walkaway & 107.832423 \\ \hline
    follow & 106.300268 \\ \hline
    red & 99.139168 \\ \hline
    maga & 95.622477 \\ \hline
    redwave & 95.294118 \\ \hline
    qanon & 86.301370 \\ \hline
    dems & 65.538736 \\ \hline
    usa & 60.909091 \\ \hline
    via & 57.861635 \\ \hline
    god & 56.432247 \\ \hline
    economy & 51.132075 \\ \hline
    \end{tabular}
    \caption{Words used more often by bots}
    \label{tab:bot-dominant-words}
\end{table}

@@

\begin{figure}[H]
    \includegraphics[width=\linewidth]{images/mostly_humans.png}
    \caption{Word used more more often by humans}
    \label{fig:humans_dominant}
\end{figure}

\begin{table}[H]
    \centering
    \begin{tabular}{|l|l|}
    \hline
    \textbf{Word} & \textbf{Percentage Difference} \\ \hline
    bunch & 58.440047 \\ \hline
    yall & 52.095130 \\ \hline
    bc & 45.844156 \\ \hline
    shot & 45.454545 \\ \hline
    woman & 43.218954 \\ \hline
    children & 41.602787 \\ \hline
    line & 41.316348 \\ \hline
    school & 41.313559 \\ \hline
    cruz & 39.701074 \\ \hline
    points & 39.238095 \\ \hline
    men & 39.154161 \\ \hline
    put & 35.545906 \\ \hline
    stay & 35.414725 \\ \hline
    ted & 35.111111 \\ \hline
    \end{tabular}
    \caption{Words used more often by humans}
    \label{tab:humans-dominant-words}
\end{table}

@@

\begin{figure}[H]
    \includegraphics[width=\linewidth]{images/emotions.png}
    \caption{Histogram of Tweet Sentiment}
    \label{fig:setiment_histogram}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \begin{subfigure}[b]{1\linewidth}
      \includegraphics[width=\linewidth]{images/bots_furtherretweeted.png}
      \caption{Bots Parents}
      \label{fig:further_retweet_bots}
    \end{subfigure}
    \begin{subfigure}[b]{1\linewidth}
      \includegraphics[width=\linewidth]{images/humans_furtherretweeted.png}
      \caption{Humans Parents}
      \label{fig:further_retweet_humans}
    \end{subfigure}
    \caption{Further Retweet}
    \label{fig:further_retweet}
  \end{figure}

@@

\begin{figure}[H]
    \includegraphics[width=\linewidth]{images/bot_humans_retweet_percentages.png}
    \caption{At Different Percentage Intervals}
    \label{fig:humans_bots_percentage}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \captionsetup{justification=centering}

@@

\begin{table}[H]
    \centering
    \begin{tabular}{|l|l|}
    \hline
    \textbf{Domain Name} & \textbf{Frequency} \\ \hline
    t.co & 127717 \\ \hline
    vote.gop & 96127 \\ \hline
    thehill.com & 57476 \\ \hline
    cnn.com & 54129 \\ \hline
    youtube.com & 51347 \\ \hline
    wtxl.com & 38124 \\ \hline
    nytimes.com & 35863 \\ \hline
    foxnews.com & 35277 \\ \hline
    instagram.com & 31634 \\ \hline
    breitbart.com & 30290 \\ \hline
    pscp.tv & 27702 \\ \hline
    \end{tabular}
    \caption{Most Common URLs}
    \label{tab:Common_urls}
\end{table}

The top 10 domains for humans and bots, apart from t.co were:
\begin{table}[H]
    \centering
    \begin{tabular}{|l|l|}
    \hline
    \textbf{Human} & \textbf{Bots} \\ \hline
    vote.gop & vote.gop \\ \hline
    thehill.com & youtube.com \\ \hline
    cnn.com & foxnews.com \\ \hline
    youtube.com & breitbart.com \\ \hline
    wtxl.com & thegatewaypundit.com \\ \hline
    nytimes.com & pscp.tv \\ \hline
    foxnews.com & cnn.com \\ \hline
    instagram.com & instagram.com \\ \hline
    breitbart.com & thehill.com \\ \hline
    pscp.tv & facebook.com \\ \hline
    \end{tabular}
    \caption{Most Common Human and Bots URL}
    \label{tab:common_human_bots}
\end{table}

@@

\begin{figure}[H]
    \includegraphics[width=\linewidth]{images/bots_influence_vs_size.png}
    \caption{Percentage of Bots and Percentage of their influence}
    \label{fig:bots_influence_vs_size}
\end{figure}

@@

\begin{table}[H]
    \centering
    \begin{tabular}{|l|l|l|l|l|}
    \hline
    \textbf{Interval} & \textbf{Size} & \textbf{Average Influence} & \textbf{Average Size} & \textbf{Ratio} \\ \hline
    0-10 & 98709 & 15.83 & 15.1 & 1.05 \\ \hline
    10-100 & 15309 & 19.67 & 14.84 & 1.33 \\ \hline
    100-500 & 1879 & 23.02 & 13.53 & 1.7 \\ \hline
    500-1k & 209 & 23.24 & 11.02 & 2.11 \\ \hline
    1k-3k & 122 & 21.53 & 9.23 & 2.33 \\ \hline
    3k-7k & 25 & 24.49 & 8.82 & 2.78 \\ \hline
    7k-40k & 5 & 14.92 & 7.77 & 1.92 \\ \hline
    \end{tabular}
    \caption{Percentage of Bots and their Influence}
    \label{tab:percentage_influence}
\end{table}

@@

\newpage

>>>>

\documentclass[letterpaper]{article}
\usepackage{aaai19}
\usepackage{times} 
\usepackage{helvet}
\usepackage{courier} 
\usepackage[hyphens]{url}
\usepackage{graphicx}
\urlstyle{rm}
\def\UrlFont{\rm}
\usepackage{graphicx}
\frenchspacing
\setlength{\pdfpagewidth}{8.5in}
\setlength{\pdfpageheight}{11in}
% custom packages%
\usepackage{amsmath}
\usepackage{enumitem}
\usepackage{subcaption}

@@

\setcounter{secnumdepth}{2} %May be changed to 1 or 2 if section numbers are desired.

@@

\section{Methods}
\label{sec:method}
\subsection{Data Collection}
Twenty-nine manually identified keywords, and names of all 53 House candidates, and 27 Senate candidates were used to collect live data from Twitter. The manually defined keywords were:

\begin{table}[]
    \centering
    \begin{tabular}{ll}
    • 2018Midterms & • resist \\
    • 2018MidtermElections & • VOTE \\
    • Election2018 & • GAEarlyVoting \\
    • ElectionDay & • EarlyVoting \\
    • MAGA2018 & • plus1 \\
    • MAGA & • IVoted \\
    • Trump2020 & • WinBlue \\
    • AmericaFirst & • WinRed \\
    • TheResistance & • BlueWave \\
    • WalkAwayFromRepublicans2018 & • RedWave \\
    • VoteThemOut & • republican2018 \\
    • 2018Senate & • democrat2018 \\
    • VoteRed & • Republican \\
    • Voteblue & • Democrat \\
    • WalkAwayFromDemocrats2018 & 
    \end{tabular}
    \caption{Manual Keywords}
    \label{tab:manual-keywords}
    \end{table}

@@

\begin{table}
    \centering
    \begin{tabular}{|l|l|}
    \hline
    \textbf{Word} & \textbf{Percentage Difference} \\ \hline
    voteredtosaveamerica & 169.715447 \\ \hline
    patriots & 161.121157 \\ \hline
    votered & 130.514988 \\ \hline
    walkaway & 107.832423 \\ \hline
    follow & 106.300268 \\ \hline
    red & 99.139168 \\ \hline
    maga & 95.622477 \\ \hline
    redwave & 95.294118 \\ \hline
    qanon & 86.301370 \\ \hline
    dems & 65.538736 \\ \hline
    usa & 60.909091 \\ \hline
    via & 57.861635 \\ \hline
    god & 56.432247 \\ \hline
    economy & 51.132075 \\ \hline
    \end{tabular}
    \caption{Words used more often by bots}
    \label{tab:bot-dominant-words}
\end{table}

@@

\begin{figure}
    \includegraphics[width=\linewidth]{images/mostly_humans.png}
    \caption{Word used more more often by humans}
    \label{fig:humans_dominant}
\end{figure}

\begin{table}
    \centering
    \begin{tabular}{|l|l|}
    \hline
    \textbf{Word} & \textbf{Percentage Difference} \\ \hline
    bunch & 58.440047 \\ \hline
    yall & 52.095130 \\ \hline
    bc & 45.844156 \\ \hline
    shot & 45.454545 \\ \hline
    woman & 43.218954 \\ \hline
    children & 41.602787 \\ \hline
    line & 41.316348 \\ \hline
    school & 41.313559 \\ \hline
    cruz & 39.701074 \\ \hline
    points & 39.238095 \\ \hline
    men & 39.154161 \\ \hline
    put & 35.545906 \\ \hline
    stay & 35.414725 \\ \hline
    ted & 35.111111 \\ \hline
    \end{tabular}
    \caption{Words used more often by humans}
    \label{tab:humans-dominant-words}
\end{table}

@@

\begin{figure}
    \includegraphics[width=\linewidth]{images/emotions.png}
    \caption{Histogram of Tweet Sentiment}
    \label{fig:setiment_histogram}
\end{figure}

@@

\begin{figure}
    \centering
    \begin{subfigure}[b]{1\linewidth}
      \includegraphics[width=\linewidth]{images/bots_furtherretweeted.png}
      \caption{Bots Parents}
      \label{fig:further_retweet_bots}
    \end{subfigure}
    \begin{subfigure}[b]{1\linewidth}
      \includegraphics[width=\linewidth]{images/humans_furtherretweeted.png}
      \caption{Humans Parents}
      \label{fig:further_retweet_humans}
    \end{subfigure}
    \caption{Further Retweet}
    \label{fig:further_retweet}
  \end{figure}

@@

\begin{figure}
    \includegraphics[width=\linewidth]{images/bot_humans_retweet_percentages.png}
    \caption{At Different Percentage Intervals}
    \label{fig:humans_bots_percentage}
\end{figure}

@@

\begin{figure}
    \centering
    \captionsetup{justification=centering}

@@

\begin{table}
    \centering
    \begin{tabular}{|l|l|}
    \hline
    \textbf{Domain Name} & \textbf{Frequency} \\ \hline
    t.co & 127717 \\ \hline
    vote.gop & 96127 \\ \hline
    thehill.com & 57476 \\ \hline
    cnn.com & 54129 \\ \hline
    youtube.com & 51347 \\ \hline
    wtxl.com & 38124 \\ \hline
    nytimes.com & 35863 \\ \hline
    foxnews.com & 35277 \\ \hline
    instagram.com & 31634 \\ \hline
    breitbart.com & 30290 \\ \hline
    pscp.tv & 27702 \\ \hline
    \end{tabular}
    \caption{Most Common URLs}
    \label{tab:Common_urls}
\end{table}

The top 10 domains for humans and bots, apart from t.co were:
\begin{table}
    \centering
    \begin{tabular}{|l|l|}
    \hline
    \textbf{Human} & \textbf{Bots} \\ \hline
    vote.gop & vote.gop \\ \hline
    thehill.com & youtube.com \\ \hline
    cnn.com & foxnews.com \\ \hline
    youtube.com & breitbart.com \\ \hline
    wtxl.com & thegatewaypundit.com \\ \hline
    nytimes.com & pscp.tv \\ \hline
    foxnews.com & cnn.com \\ \hline
    instagram.com & instagram.com \\ \hline
    breitbart.com & thehill.com \\ \hline
    pscp.tv & facebook.com \\ \hline
    \end{tabular}
    \caption{Most Common Human and Bots URL}
    \label{tab:common_human_bots}
\end{table}

@@

\begin{figure}
    \includegraphics[width=\linewidth]{images/bots_influence_vs_size.png}
    \caption{Percentage of Bots and Percentage of their influence}
    \label{fig:bots_influence_vs_size}
\end{figure}

@@

\begin{table}
    \centering
    \begin{tabular}{|l|l|l|l|l|}
    \hline
    \textbf{Interval} & \textbf{Size} & \textbf{Average Influence} & \textbf{Average Size} & \textbf{Ratio} \\ \hline
    0-10 & 98709 & 15.83 & 15.1 & 1.05 \\ \hline
    10-100 & 15309 & 19.67 & 14.84 & 1.33 \\ \hline
    100-500 & 1879 & 23.02 & 13.53 & 1.7 \\ \hline
    500-1k & 209 & 23.24 & 11.02 & 2.11 \\ \hline
    1k-3k & 122 & 21.53 & 9.23 & 2.33 \\ \hline
    3k-7k & 25 & 24.49 & 8.82 & 2.78 \\ \hline
    7k-40k & 5 & 14.92 & 7.77 & 1.92 \\ \hline
    \end{tabular}
    \caption{Percentage of Bots and their Influence}
    \label{tab:percentage_influence}
\end{table}

@@
